### 2022-08-09 preprint.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@19d988557e6f7228fa28bc84dd766f7a35ae8383 🚀

\begin{figure}
\hypertarget{fig:measures}{%
\centering
\includegraphics{figures/measures_emp_maxent.png}
\caption{Relationship between the structure of empirical and maximum
entropy food webs. Empirical networks include all food webs archived on
Mangal, as well as the New-Zealand and Tuesday lake datasets (our
complete dataset). Maximum entropy networks were estimated using a
simulated annealing algorithm to find the network of maximum SVD entropy
while maintaining the joint degree sequence (type II MaxEnt network
model). (a) Nestedness (estimated using the spectral radius of the
adjacency matrix), (b) the maximum trophic level, (c) the network
diameter, and (d) the SVD entropy were measured on these empirical and
maximum entropy food webs. The identity line is plotted in each
panel.}\label{fig:measures}
}
\end{figure}

@@

>>>>

\begin{figure}
\hypertarget{fig:measures}{%
\centering
\includegraphics{figures/measures_emp_maxent.png}
\caption{Relationship between the structure of empirical and maximum
entropy food webs. Empirical networks include all food webs archived on
Mangal, as well as the New-Zealand and Tuesday Lake datasets (our
complete dataset). Maximum entropy networks were estimated using a
simulated annealing algorithm to find the network of maximum SVD entropy
while maintaining the joint degree sequence (type II MaxEnt network
model). (a) Nestedness (estimated using the spectral radius of the
adjacency matrix), (b) the maximum trophic level, (c) the network
diameter, and (d) the SVD entropy were measured on these empirical and
maximum entropy food webs. The identity line is plotted in each
panel.}\label{fig:measures}
}
\end{figure}

@@

\leavevmode\hypertarget{ref-Poisot2021GloKno}{}%
Poisot, Timothée, Gabriel Bergeron, Kevin Cazelles, Tad Dallas,
Dominique Gravel, Andrew MacDonald, Benjamin Mercier, Clément Violet,
and Steve Vissault. 2021. {``Global Knowledge Gaps in Species
Interaction Networks Data.''} \emph{Journal of Biogeography} 48 (7):
1552--63. \url{https://doi.org/10.1111/jbi.14127}.
